InteroceptionStudy_GPValidation

### 2021-08-27 IAPS_PREPROCESSING_2021_1.Rmd
Update IAPS_PREPROCESSING_2021_1.Rmd

db_HR_bio1<- subset(db_HR_bio,db_HR_bio$trigger2< 100)

db_HR_bio1<- db_HR_bio1%>%
  arrange(ssid, as.numeric(timestart))

@@

db_HR_bio1no328<-subset(db_HR_bio1, db_HR_bio1$ssid!= 328)
db_HR_bio1no328<- subset(db_HR_bio1no328, trigger2> 15 & trigger2<72)

db_HR_bio1no328<- db_HR_bio1no328 %>%
  arrange(ssid, trigger2)%>%
  filter(!duplicated(trigger2))

db_HR_bio1no328<- db_HR_bio1no328 %>%
  group_by(ssid)%>%
  mutate(tNo = -6:(n()-7)) #56 trials

@@

tmp.df4_sum_full_bio_hr_self_parsed1<- select(tmp.df4_sum_full_bio_hr_self_parsed,)

>>>>

# this will delete fixation and stuff so no
# db_HR_bio1<- subset(db_HR_bio,db_HR_bio$trigger2< 100)

db_HR_bio1<- db_HR_bio%>%
  arrange(ssid, as.numeric(timestart))

@@

db_HR_bio1no328<-subset(db_HR_bio1, db_HR_bio1$ssid!= 328)

db_HR_bio1no328$trigger2
db_HR_bio1no328<- subset(db_HR_bio1no328, trigger2> 15 & trigger2<106)

db_HR_bio1no328$trigger<- db_HR_bio1no328$tNo
# db_HR_bio1no328

# db_HR_bio1no328<- db_HR_bio1no328 %>%
#   arrange(ssid, trigger2)%>%
#   filter(!duplicated(trigger2))

View(trigger)
db_HR_bio1no328<- db_HR_bio1no328$t %>%
  group_by(ssid)%>%
  mutate(tNo =  -6:(n()-7)) #56 trials

@@

# tmp.df4_sum_full_bio_hr_self_parsed1<- select(tmp.df4_sum_full_bio_hr_self_parsed,)
